An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
reviewed Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{At the present work, the focus is not a novelty in the criteria or the optimization objectives. Our aim and novelty is to show a most effective approach on the pursuit of the optimal solution, using formal methods.}

@@

Our work makes two major contributions. \textbf{Firstly}, the use of automated 
symbolic verification methods in electrical systems was uncommon in recent 
prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
method together with user requirements and environment constraints, 
and our synthesis algorithm based on symbolic model checking 
can find the optimal solution in technical and economical terms. 
\textbf{Secondly}, we evaluate different state-of-art symbolic software 
verifiers with the goal of obtaining the best performance in our verification 
back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}

\textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
Section~\ref{sec:Method} presents the automated formal synthesis proposed 
in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:Background}
%-----------------------------------------------------------

>>>>

\textcolor{red}{In this study, our focus is not on a novel criteria or optimization objectives. Instead, our novelty relies on an effective approach on the pursuit of the optimal solution using formal methods, which outperforms existing state-of-the-art simulation tools.}

@@

%------------------------------------------------------
\subsection{Contributions}
%------------------------------------------------------

Our work makes three major contributions. \textbf{First}, the use of automated 
symbolic verification methods in electrical systems was uncommon in recent 
prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
method together with user requirements and environment constraints, 
and our synthesis algorithm based on symbolic model checking 
can find the optimal solution in technical and economical terms. 
\textbf{Second}, we evaluate different state-of-art symbolic software 
verifiers with the goal of obtaining the best performance in our verification 
back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}
\textcolor{red}{\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
on the pursuit of the optimal solution of PV system design using formal methods, which outperforms 
existing state-of-the-art simulation tools.}

\noindent \textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
Section~\ref{sec:Method} presents the automated formal synthesis proposed 
in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:Background}
%-----------------------------------------------------------
